Classical Planning with Simulators: \\ Results on the Atari Video Games

### 2015-02-09 ijcai15-paper/paper.tex
nir comments

@@

\title{Classical Planning with Simulations: \\ Results on the Atari Video Games}

@@

The action selection problem in the Atari games can be seen as a \emph{reinforcement learning} problem
\cite{sutton:book} over a deterministic MDP where the state transitions and rewards are not known, or alternatively,
as a  \emph{net-benefit planning problem} \cite{coles2012survey,keyder:jair09} with unknown state transitions  and  rewards. 
Namely, we seek  an action sequence $a_0, a_1, \ldots, a_m$ from the  current  state $s_0$ that generates
a state sequence $s_0, s_1, \ldots, s_{m+1}$ with  maximum  total reward $\sum_{i=0}^{m} r(a_i,s_i)$,
where $m$ is a sufficiently large planning horizon, and the rewards $r(a_i,s_i)$ and the  state-transitions $s_{i+1}=f(a_i,s_i)$
are known only after  action $a_i$ is applied in the state $s_i$.

>>>>

\usepackage{todonotes}
\newcommand{\nir}{\todo[inline,color=orange!10]}
\newcommand{\hg}{\todo[color=blue!10]}
\newcommand{\mrj}{\todo[inline,color=green!10]}

@@

\title{Classical Planning with Simulators: \\ Results on the Atari Video Games}

@@

The action selection problem in the Atari games can be seen as a \emph{reinforcement learning} problem
\cite{sutton:book} over a deterministic MDP where the state transitions and rewards are not known, or alternatively,
as a  \emph{net-benefit planning problem} \cite{coles2012survey,keyder:jair09} with unknown state transitions  and  rewards. 
\Omit{Namely}
\nir{While the \emph{reinforcement learning} problem seeks to synthesize a controller as a policy/function that maximizes 
the reward of any trajectory}, we seek  an action sequence $a_0, a_1, \ldots, a_m$ from the  current  state $s_0$ that generates
a state sequence $s_0, s_1, \ldots, s_{m+1}$ with  maximum  total reward $\sum_{i=0}^{m} r(a_i,s_i)$,
where $m$ is a sufficiently large planning horizon, and the rewards $r(a_i,s_i)$ and the  state-transitions $s_{i+1}=f(a_i,s_i)$
are known only after  action $a_i$ is applied in the state $s_i$.
